### 2021-03-05 test_slide.Rmd

---
subtitle: "2020年底魚類現存量調査結果"
author: "金森由妃・成松庸二・鈴木勇人・森川英祐・時岡　駿・三澤　遼・永尾次郎"
date: "2021/3/10"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r-test, include=FALSE}
require(tidyverse)
require(openxlsx)

# directory -----------------------------------------------------
dir_input = "/Users/Yuki/Dropbox/業務/若鷹丸調査結果まとめ_東北底魚研究/2020年度/input"
dir_output = "/Users/Yuki/Dropbox/業務/若鷹丸調査結果まとめ_東北底魚研究/2020年度/output"

# data ----------------------------------------------------------
old = NULL
for(i in 1:(2018-1995+1)){
  temp = read.xlsx(paste0(dir_input, "/1_1995～2018資源尾数、重量グラフ.xlsx"), sheet = i, startRow = 1)

  if(i < 12){
    temp = temp[, c(1:5, 7:9)]
    temp = temp %>% na.omit() %>% filter(南北 != "南北計")
  }else{
    temp = temp[, 1:8]
    temp = temp %>% na.omit() %>% filter(南北 != "南北計")
  }

  old = rbind(old, temp)
}

y19 = read.xlsx(paste0(dir_input, "/q_資源量合計クエリ2019.xlsx"), sheet = 1, startRow = 1) %>% na.omit() %>% filter(南北 != "南北計")
y20 = read.xlsx(paste0(dir_input, "/q_資源量合計クエリ2020.xlsx"), sheet = 1, startRow = 1) %>% na.omit() %>% filter(南北 != "南北計")

all = rbind(old, y19, y20)
all = all %>% mutate(year = as.numeric(str_sub(調査種類名称, 1, 4)), NS = str_sub(南北, 1, 1)) %>% dplyr::rename(data = "尾数・重量", sp = "和名", sum = "資源量計") %>% select(year, NS, data, sp, sum)
ns = data.frame(NS = c("N", "S"), 南北 = c("北部", "南部"))
all = left_join(all, ns, by = "NS") %>% select(-NS) %>% dplyr::rename(NS = 南北)
all$NS = factor(all$NS, levels = c("北部", "南部"))
all = all %>% mutate(data = ifelse(all$data == "資源重量", "重量", "尾数"))
```
```{r-test2}
unique(all$sp)
```

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## 調査の概要
- 日時
  - 2020年10月1日〜11月13日
- 場所

```{fig1, fig.align='right', fig.height = 3}
setwd("/Users/Yuki/Dropbox/業務/若鷹丸調査結果まとめ_東北底魚研究/2020年度/output")
knitr::include_graphics("fig1.png")
```

## スケトウダラ0歳
```{suke0_trend, fig.align='centor'}
setwd("/Users/Yuki/Dropbox/業務/若鷹丸調査結果まとめ_東北底魚研究/2020年度/output")
knitr::include_graphics("スケトウダラ０＋trend.png")
```